---
title: "R Notebook"
output: html_notebook
---

# install packages
```{r}
#install.packages("tidyverse",dependencies = TRUE)
#install.packages("ggthemes",dependencies = TRUE)
```

# load packages
```{r}
library(tidyverse)
library(ggthemes)
```

# rows and columns
```{r}
as4 = read_csv("assignment4.csv")

nrow(as4)
ncol(as4)

# There are 3700 rows and 12 columns.
```

# unique participants and trials
```{r}
as4 %>% pull (subject) %>% unique()

as4 %>%
  group_by(subject) %>% 
  count()

# There were 37 subjects.
# Each subject had 100 trials.
```

# Level of variables
```{r}
as4 = as4 %>%
  mutate(prime_condition = as.factor(prime_condition), 
         state = as.factor(state))

levels (as4 %>% pull (prime_condition))

levels (as4 %>% pull (state))

# There are 4 levels of prime_condition: "both","phonological","semantic", and 'unrelated."
# There are 4 levels of the state variable: "don't know","know","other", and "tip of tongue."
```

# subsets of columns
```{r}
prime_information = as4 %>%
  select(subject, prime_condition)
```

# subsets of rows
```{r}
phonological = as4 %>%
  filter(prime_condition=="phonological" & accuracy==1)
```

# summarizing accuracy per subject
```{r}
subject_acc = as4 %>%
  group_by(subject) %>%
  summarise(mean_acc = mean(accuracy))
```

# Summarizing accuracy per prime condition
```{r}
prime_acc = as4 %>%
  group_by(prime_condition) %>%
  summarise(mean_acc = mean(accuracy),
            sd_acc = sd(accuracy))
```

# histogram of subject accuracy
```{r}
subject_acc %>%
  ggplot(aes(x=mean_acc)) +
  geom_histogram(binwidth = .2,
                 fill = "tan", 
                 color = "black",
                 position = "identity") +
  theme_few() + 
  xlab("Mean Accuracy") +
  ylab("Count") +
  ggtitle("Histogram of Mean Accuracy")
```

# bar plot of prime condition
```{r}
prime_acc %>%
  ggplot(aes(x = prime_condition, y = mean_acc)) +
  geom_bar(fill = "pink", color = "blue", stat = "identity") +
  theme_few() + 
  xlab("Prime Condition") +
  ylab("Mean Accuracy") +
  ggtitle ("Mean Accuracy Across Prime Condition")
```

# Data interpretation
```{r}
# Yes, the type of prime influences accuracy in the trivia experiment. It seems like after a phonological prime condition, participants were significantly more likely to have an accurate response, compared to "both", "semantic", or "unrelated."
```

# Summarizing accuracy per prime condition and state
```{r}
state_prime_acc = as4 %>%
  group_by(state, prime_condition) %>%
  summarise(mean_acc = mean(accuracy))
```

# bar plot of prime condition and state
```{r}
state_prime_acc %>%
  ggplot(aes(x = prime_condition, y = mean_acc, fill = state)) +
  geom_col(position = "dodge") +
  theme_few() +
  labs(x = "Prime Condition", y = "Mean Accuracy", title = "Mean Accuracy Across Prime Condition and Reported States")
```



